Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study

### 2021-03-01 submission/manuscript.rmd
incorporate risk stratified plot for hip fracture

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(pander)
library(knitr)

@@

>>>>

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(knitr)

@@

\newpage
```{r plotAbsoluteHip, echo=FALSE, fig.cap="This is a caption", out.width = '100%'}
knitr::include_graphics(here::here("figures/plotAbsoluteHip.png"))
```
